Universal Anonymous Signatures

### 2022-08-21 prism-backend/research/gsac/app-uas-proofs.tex
Updated correctness.

\begin{proof}[\thmref{thm:correctness-uas}; Correctness of \CUASGen]
  By correctness of \SBCM and the NIZK for $\NIZKRel_{\Sign}$, the signature
  produced at line 5 of \ExpCorrect is accepted at line 6 by \Verify.
  Moreover, all the credentials employed to honestly produce the signature,
  identified with \scid, meet their respective issuance policies due to
  correctness of the NIZK for $\NIZKRel_{\Issue}$, so no $\fissue^\cid$ check
  returns $0$ at line 9. Similarly, as $\feval \in \famfeval$ is checked at
  line 3, and due to correctness of the NIZK for $\NIZKRel_{\Sign}$, the
  output of \feval matches $\yeval^0$ at line $11$, which must have been
  computed over $\usk=\UK[\uid]$, as in line $10$, due to correctness of the
  commitment scheme. Finally, correctness of the NIZKs for $\NIZKRel_{\Sign}$
  and $\NIZKRel_{\Open}$, and correctness of the encryption scheme, ensure that
  \Judge accepts the proof produced by \Open, and \yinsp is the correct value
  for the chosen $\finsp^{\oid}$.
\end{proof}

>>>>

\begin{proof}[\thmref{thm:correctness-uas}; Correctness of \CUASGen]
  By correctness of \SBCM and the NIZK for \RelSig, the signature
  produced at line 4 of \ExpCorrect is accepted at line 5 by \Verify.
  Moreover, all the credentials employed to honestly produce the signature,
  identified with \scid, meet their respective (honest) issuance policies due to
  correctness of the NIZK for \RelIss, so no $\fissue^{\cid}$ check
  returns $\neq \yissue^i$ at line 10. Similarly, as $\feval \in \famfeval$ is
  checked at line 3, and due to correctness of the NIZK for \RelSig,
  the output of \feval matches \yeval at line $12$. Finally, correctness of the
  NIZKs for \RelSig and \RelIns, and correctness of the encryption scheme,
  ensure that \Judge accepts the proof produced by \Open, and \yinsp is the
  correct value for the (honestly) chosen \finsp.
\end{proof}
